### 2018-04-02 dissertation/3-vanets/chapter3.tex
Added conclusion to Chap3 and added section 4.6.1
Small addition to chapter 3 and added algorithms to chapter 4.6

%conclude
\autoref{table:properties} shows how well each studied trust model satisfies the eight properties described in \autoref{section:properties}.

>>>>

%conclude
\autoref{table:properties} shows how well each studied trust model satisfies the eight properties described in \autoref{section:properties}.
The numbers used in the table are the same ones from \autoref{section:properties}.
This analysis shows that, although several previously proposed trust models provide reasonable solutions to the trust management problem, all of them have issues in terms of correctness, completeness or efficiency, indicating that the problem is not yet truly solved.

### 2018-04-02 dissertation/4-project/chapter4.tex
Small addition to chapter 3 and added algorithms to chapter 4.6

\State \textbf{color} all nodes of $G$ \textbf{with} 0
\State $d \rightarrow 0$
\For{$e=(u,v)$ \textbf{in} edges of $G$}
	\If{$u$ and $v$ have the same color}
		\If{$color[v] = d$}
			\State $d \rightarrow d+1$
		\EndIf
		\State $color[v] \rightarrow d$
	\EndIf
\EndFor

@@

At first, the node collects and organizes information.
A prerequisite of this step is a test that correctly classifies a neighboring node as benign or malicious.
There are several ways to perform such a test, but a study between these methods is beyond the scope of this paper.
Every time a neighboring node $v$ is tested as benign, the value of $u \rightarrow v$ increases.
Additionally, node $u$ performs an union between its trust graph and $v$'s trust graph, forming a new graph $T^u_i = T^u_{i-1} \bigcup T^v_{i-1}$, which is used for the remaining steps.

@@

Then, when node $u$ interacts with another node $w$ in the future, $u$'s opinion of $v$ comes with the timestamp attached, so $w$ has the information to know how much time has passed since the interaction between $u$ and $v$ happened.
Once $w$ performs the graph merge procedure with $T_u$ and $T_w$, but $T_w$ already has an edge $u\rightarrow v$ stored, it checks the two timestamps and only updates the edge if the incoming information is more recent than what is already stored.
Since the timestamp is always set to the destination node of the edge, it can be used for comparison regardless of which nodes handled the information. 
%This was implemented as an additional feature of TruMan, and was not used on every test.

>>>>

\State \textbf{color} all nodes of $G$ \textbf{with} 0
\State $d \gets 0$
\For{$e=(u,v)$ \textbf{in} edges of $G$}
	\If{$u$ and $v$ have the same color}
		\If{$color[v] = d$}
			\State $d \gets d+1$
		\EndIf
		\State $color[v] \gets d$
	\EndIf
\EndFor

@@

At first, the node collects and organizes information.
A prerequisite of this step is a test that correctly classifies a neighboring node as benign or malicious.
There are several ways to perform such a test, but a study between these methods is beyond the scope of this paper.
Every time a neighboring node $v$ is tested as benign, the value of $u \rightarrow v$ increases.
Additionally, node $u$ performs an union between its trust graph and $v$'s trust graph, forming a new graph $T^u_i = T^u_{i-1} \bigcup T^v_{i-1}$, which is used for the remaining steps.
Algorithm  \autoref{algorithm:interaction} shows the basic interaction between two nodes, while algorithm \autoref{algorithm:union} details the steps of the graph union.

\begin{algorithm}
\caption{Interaction between two nodes}\label{algorithm:interaction}
\begin{algorithmic}[1]

\Function{Interaction}{node $u$, node $v$}

\If{$v\notin T^u$}
	\State \textbf{add} $v$ \textbf{to} $T^u$
	\State \textbf{add} $u\rightarrow v$ \textbf{to} $T^u$
	\State $T^u(u\rightarrow v).trustvalue = 0.5$
	\State $T^u(u\rightarrow v).timestamp = $ \textbf{now}
\EndIf

\State $u$ \textbf{tests} $v$

\If{$v$ is benign}
	\State $T^u(u\rightarrow v).trustvalue$ \textbf{increases}
	\State \textbf{Union}($T^u$, $T^v$)
\Else
	\State $T^u(u\rightarrow v).trustvalue$ \textbf{decreases}
\EndIf

\begin{algorithm}
\caption{Graph union}\label{algorithm:union}
\begin{algorithmic}[1]

\Function{Union}{graph $T^u$, graph $T^v$}

\For{$a\rightarrow b$ \textbf{in} edges of $T^v$ }

	\If{$a\notin T^u$}
		\State \textbf{add} $a$ \textbf{to} $T^u$
	\EndIf

	\If{$b\notin T^u$}
		\State \textbf{add} $b$ \textbf{to} $T^u$
	\EndIf

	\If{$a\rightarrow b \notin T^u$}
		\State \textbf{add} $a\rightarrow b$ \textbf{to} $T^u$
	\EndIf
\EndFor

@@

Then, when node $u$ interacts with another node $w$ in the future, $u$'s opinion of $v$ comes with the timestamp attached, so $w$ has the information to know how much time has passed since the interaction between $u$ and $v$ happened.
Once $w$ performs the graph merge procedure with $T_u$ and $T_w$, but $T_w$ already has an edge $u\rightarrow v$ stored, it checks the two timestamps and only updates the edge if the incoming information is more recent than what is already stored.
Since the timestamp is always set to the destination node of the edge, it can be used for comparison regardless of which nodes handled the information. 
Algorithm \autoref{algorithm:union_timestamp} shows how the union function was changed to accommodate timestamps and information aging.

\begin{algorithm}
\caption{Graph union with timestamps}\label{algorithm:union_timestamp}
\begin{algorithmic}[1]

\Function{Union}{graph $T^u$, graph $T^v$}

\For{$a\rightarrow b$ \textbf{in} edges of $T^v$ }

	\If{$a\notin T^u$}
		\State \textbf{add} $a$ \textbf{to} $T^u$
	\EndIf

	\If{$b\notin T^u$}
		\State \textbf{add} $b$ \textbf{to} $T^u$
	\EndIf

	\If{$a\rightarrow b \notin T^u$}
		\State \textbf{add} $a\rightarrow b$ \textbf{to} $T^u$
	\Else
		\State $s_0 \gets T^u(a\rightarrow b).timestamp$
		\State $s_1 \gets T^v(a\rightarrow b).timestamp$
		\If{$s_1$ \textbf{is more recent than} $s_0$}
			\State $T^u(a\rightarrow b).trustvalue \gets T^v(a\rightarrow b).trustvalue$
			\State $T^u(a\rightarrow b).timestamp \gets T^v(a\rightarrow b).timestamp$
		\EndIf	
	\EndIf
\EndFor
